Meta-analysis

### 2020-06-04 04_MetaAnalysis.Rmd
Don't evaluate pval_iteration chunk

```{r pval_iteration_plot}
# Plot the p - values of the spray_management moderators
# transform y axis on log scale
metaI %>%
   ggplot(aes(x = iteration , y = pval, )) +
   geom_line() +
   scale_y_log10() +
   geom_hline(
      yintercept = c(0.05, 0.001),
      colour = "grey50",
      linetype = 2
   ) +
   facet_grid(cols = vars(mods),
              labeller = labeller(mods = change_labels)) +
   theme(strip.text.x = element_text(size = 9)) +
   geom_text(
      aes(
         y = 0.05,
         x = 1,
         label = c("P = 0.05")
      ),
      size = 3,
      colour = "grey50",
      hjust = 0,
      vjust = -0.5
   )+
      geom_text(
      aes(
         y = 0.001,
         x = 1,
         label = c("P = 0.001")
      ),
      size = 3,
      colour = "grey50",
      hjust = 0,
      vjust = -0.5
   )

@@

```{r metafor_summary}
summary(PM_mv_AI)
rstudent.rma.mv(PM_mv_AI)
# confint(PM_mv_AI) Can't finish running
```

>>>>

```{r pval_iteration_plot, eval=FALSE, include=FALSE}
# Plot the p - values of the spray_management moderators
# transform y axis on log scale
metaI %>%
   ggplot(aes(x = iteration , y = pval, )) +
   geom_line() +
   scale_y_log10() +
   geom_hline(
      yintercept = c(0.05, 0.001),
      colour = "grey50",
      linetype = 2
   ) +
   facet_grid(cols = vars(mods),
              labeller = labeller(mods = change_labels)) +
   theme(strip.text.x = element_text(size = 9)) +
   geom_text(
      aes(
         y = 0.05,
         x = 1,
         label = c("P = 0.05")
      ),
      size = 3,
      colour = "grey50",
      hjust = 0,
      vjust = -0.5
   )+
      geom_text(
      aes(
         y = 0.001,
         x = 1,
         label = c("P = 0.001")
      ),
      size = 3,
      colour = "grey50",
      hjust = 0,
      vjust = -0.5
   )

@@

```{r metafor_summary}
summary(PM_mv_AI)
```
